Analysis of split plot design using MCMCglmm

### 2017-07-31 Analysis.Rmd
Update for dplyr 0.7; fix munging issues in DS2015 data; generate new graphs

In 2015 and 2016 the highest N treatment was significant in both the tiller sheath blight incidence and severity. In 2016 the flooding treatment was significant for tiller sheath blight severity.

@@

In 2015 no significant itneraction was observed. In 2016 a significant interaction between flooding and nitrogen rate is observed for both the tiller and leaf severity ratings.

>>>>

In 2015 and 2016 the highest N treatments (note that they were different amounts
in these two years) were significant in both the tiller
sheath blight incidence and severity. In 2016 the flooding treatment was
significant for tiller sheath blight severity.

@@

In 2015 no significant interaction was observed. In 2016 a significant interaction between flooding and nitrogen rate is observed for both the tiller and leaf severity ratings.
